Ensuring Fairness with Transparent Auditing of Ethical Bias in AI Systems\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-04-24 abstract.tex
Added compas intro

\section{Ease of Use}
bias sources example (COMPAS)
fairness is subjective, based on culture and often not quantitative
for AI system we use quantitative fairness measures
transparency and objectivity example : COMPAS
third party needed for auditing example : propublica like entity can use our stuff; we're not replacing but supplement; domain knowledge
we propose a framework

>>>>

AI system, however, may be biased. Factors such as inherent biases in original data sets or flaws in algorithm designs could contribute to bias within AI systems. When left unchecked, the ramifications of such biases extend far beyond mere inaccuracies; it can lead to devastating consequences, such as amplifying systemic injustices, perpetuating group discrimination, and exacerbating societal inequalities.

Correctional Offender Management Profiling for Alternative Sanctions (COMPAS) is a tool for predicting recidivism---the tendency of criminals to reoffend. It is used in the criminal justice system in multiple states in the United States. In 2016, it was discovered in an investigation by the journalists at ProPublica that the COMPAS system is, in fact, unfair towards minority and disadvantaged groups.

\section{Ease of Use}
fairness is subjective, based on culture and often not quantitative
for AI system we use quantitative fairness measures
transparency and objectivity example : COMPAS
third party needed for auditing example : propublica like entity can use our stuff; we're not replacing but supplement; domain knowledge
we propose a framework
